%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.5cm}
{\Large \textbf{Posters}}\\[-0.4cm]
\makebox[\linewidth]{\rule{1.0\textwidth}{0.4pt}}\\
\vspace{.05cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{addmargin}[0.5cm]{0cm}
\tab[-0.5cm]\href{https://schuyler-smith.github.io/posters/phylosmith}{{\color{black}\textbf{Smith, S.D.} 
    \textit{phylosmith: an R-package for reproducible and efficient microbiome analysis with \\[-0.1cm] 
    phyloseq-objects}. {Presented at the 27th ISMB/18th ECCB. 2019, July 21-25. Basel, Switzerland.}}} \\
\tab[-0.5cm]\href{https://schuyler-smith.github.io/posters/isme_2018}{{\color{black}\textbf{Smith, S.D.}, 
    Villanueva, P.E., Fukami, T., Howe, A. \textit{Co-Occurrence Networks Reveal Key OTUs in Flower \\[-0.1cm] 
    Nectar Microbiomes Across Dispersal Treatments}. {Presented at the 17th ISME. 2018, August 12-17. \\[-0.1cm] 
    Leipzig, Germany \& the NSF Research Traineeship (NRT) Annual Meeting. 2018, September 27-28. \\[-0.1cm] Arlington, Virginia.}}} \\
\tab[-0.5cm]\href{https://schuyler-smith.github.io/posters/p3_2017}{{\color{black}\textbf{Smith, S.D.}, 
    Howe, A. \textit{Examining Antibiotic Resistance Gene (ARG) horizontal transfer and introduction \\[-0.1cm] 
    through farmland soil microbiomes as a result of modern farming practices}. {Presented at the 3rd \\[-0.1cm] 
    Annual Front Rang Computational \& Systems Biology Symposium: Microbiome. 2017, June 12-13. \\[-0.1cm]
    Fort Collins, Colorado}.}} \\
\tab[-0.5cm]\href{https://schuyler-smith.github.io/posters/icqg_2016}{{\color{black}\textbf{Smith, S.D.}, 
    Endelman, J.B. \textit{Genotyping by Sequencing for Autotetraploid Species}. {Presented at the 5th \\[-0.1cm] 
    International Conference on Quantitative Genetics. 2016, June 12-17. Madison, Wisconsin. \& the 11th \\[-0.1cm] 
    Annual National Association of Plant Breeders Meeting. 2016, August 15-18. Raleigh, North Carolina}.}}\\
\end{addmargin}
