\section*{Select Projects}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\Project}[3]{%
  \noindent\textbf{#1} \hfill \textit{#2}\\
  \begin{addmargin}[1cm]{1cm}
    #3
  \end{addmargin}
  \vspace{0.2cm}
}

\Project
  {Soil Laboratory Quality Control Automation}
  {Python, scikit-learn, regression, random forest, XGBoost}
  {Implemented machine learning models to detect failed samples in laboratory pipelines, reducing manual review time and improving client turnaround.}

\Project
  {Scalable Metagenomics Pipeline}
  {NextFlow, Airflow, AWS, Docker, DIAMOND, Kraken, MEGAN}
  {Developed a reproducible pipeline for large-scale soil microbiome sequencing and annotation, reducing runtime by 40\% and enabling processing of terabyte-scale datasets.}

\Project
  {qPCR Quality Control Tool}
  {\CC, Python, Dash, plotly, AWS, GCP, Docker}
  {Designed and created a CLI \CC software for automated quality control of qPCR data, reducing manual review time and improving data accuracy for downstream analysis. Then developed an interactive dashboard for visualizing qPCR results and trends over time.}

\Project
  {Soil-Biome Report}
  {Python, Figma, Docker, AWS, gRPC, PostgreSQL}
  {Worked with team to design a PDF report for customers who wanted soil-biome analysis. Authored the python package implemented in gRPC for processing the biome data for the report format.}

\Project
  {Soil Biological Product Recommendation System}
  {Python, Dash, Docker, GCP, Gemini, RAG, GenAI}
  {Built a recommendation platform integrating RAG and GenAI to suggest soil biological products based on microbiome profiles and crop type, enabling more data-driven and customized client decisions.}

\Project
  {Product Trial Analyses}
  {R, R Markdown, ggplot2, Jupyter Notebooks}
  {Analyzed agricultural product trial datasets and generated reproducible reports for internal teams and external stakeholders, supporting product development and strategy decisions.}
